\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage[toc,page]{appendix}

\title{Autonomous Agents \\ Assignment 1 \\ Group 2}
\author{Louis Smit (10678697) \\ Jerome Cremers (10470425) \\
Hubert Szostek (10656804) \\ Lex Utama (10660356)}
\date{September 2013}

\begin{document}

\maketitle 

\section{Introduction}
In this assignment several single agent planning methods are implemented on a predator-prey game, as described in the assignment. The basic environment is an 11x11 grid. The grid is
toroidal: the north side of the grid is attached to the south side, and the east side is attached to the west side. The predator and the prey can be anywhere on this grid, though they cannot be on the same square. The starting position of the prey is (5,5) and that of the predator (0,0).\\
Obviously, the goal for the predator is to catch the prey. This happens when the predator stands next to the prey, and moves in the direction of the prey. When the prey is captured, the episode ends, and the game is reverted to the starting position.


\section{Implementation}
The game is implemented in Java. Eclipse was used as a code editor and compiler. \\
Classes\\
State space representation\\

\subsection{Value Iteration}
\input{sections/implementation/valueiteration.tex}

\subsection{Policy Evalutation}
\input{sections/implementation/policyevaluation.tex}


\section{Application Manual}
\input {sections/manual.tex}

\section{Results}
\label{sec:results}
\subsection{Assignment 1.1}
We successfully implemented the simulator and measured the following statistics: 

\begin{verbatim}
Average: 130.304, standard deviation: 226.82542093865914
\end{verbatim}
\subsection{Assignment 1.2}
\input{sections/results/1.2.tex}

\subsection{Assignment 1.3/4} 

Numbers of iterations for different values of gamma are presented in the table below. 

\begin{longtable}
{| p{.30\textwidth}| p{.30\textwidth} | p{.30\textwidth} |} 
   Gamma & VI iterations & PI iterations \\
    \hline
0.1 & 6 & 12 \\ 
0.5 & 13& 20 \\
0.7 & 15& 28\\
0.9 &17 &  54\\
\caption{Convergance planning algorithms} 
\label{tab:myfirstlongtable}
\end{longtable}

One can see that the convergance speed ratio between the algorithms tips in favor of value iteration as gamma increases.

See appendix for state printouts.

\subsection{Assignment 1.5}
\input{sections/results/1.5.tex}


\begin{appendices}
	\input{sections/results/1.4.tex}
\end{appendices}

\end{document}
